### 2022-04-18 paper/ase22/experiment.tex
answering approach comment
paper

\section{Experiment}
\label{sec:experiment}
%
In this section, we present experiments to evaluate the effectiveness
of our proposed evaluation methodology. In particular, we address the
following research questions:

\begin{enumerate}[label=\textbf{RQ\arabic*}]
\item \label{rq:one}: How effective is our proposed evaluation model
  for finding failures given a linguistic capability?
\item \label{rq:two}: How effective is our proposed model for
  generating diverse test cases? % self bleu score
\item \label{rq:three}: How effective is test cases generated from our
  proposed model for detecting diverse type of errors? % retraining
  acc score
\item \label{rq:four}: How effective is our new test case generation
  using \cfg expansion? % ablation study
\end{enumerate}

>>>>

\section{Experiment}
\label{sec:experiment}
%

\InputWithSpace{tables/retrain-debug-table}

In this section, we present experiments to evaluate the effectiveness
of our proposed evaluation methodology. In particular, we address the
following research questions:

\begin{enumerate}[label=\textbf{RQ\arabic*}]
\item \label{rq:one}: How effective is our proposed evaluation model
  for finding failures given a linguistic capability?
\item \label{rq:two}: Can \tool be useful to find root of bug in the
  NLP models?
\item \label{rq:three}: How effective is our new test case generation
  using \cfg expansion? % ablation study
\end{enumerate}

### 2022-04-18 paper/ase22/tables/retrain-debug-numbers.tex
paper

\DefMacro{retrain_debug_retrained_lc_50}{used to  but now}

@@

\DefMacro{retrain_debug_retrained_lc_51}{used to  but now}

@@

\DefMacro{retrain_debug_retrained_lc_52}{used to  but now}

@@

\DefMacro{retrain_debug_retrained_lc_53}{used to  but now}

@@

\DefMacro{retrain_debug_retrained_lc_54}{used to  but now}

@@

\DefMacro{retrain_debug_retrained_lc_55}{used to  but now}

@@

\DefMacro{retrain_debug_retrained_lc_56}{used to  but now}

@@

\DefMacro{retrain_debug_retrained_lc_57}{simple negations: not neutral is still neutral}

@@

\DefMacro{retrain_debug_retrained_lc_58}{simple negations: not neutral is still neutral}

@@

\DefMacro{retrain_debug_retrained_lc_59}{simple negations: not neutral is still neutral}

@@

\DefMacro{retrain_debug_retrained_lc_60}{simple negations: not neutral is still neutral}

@@

\DefMacro{retrain_debug_retrained_lc_61}{simple negations: not neutral is still neutral}

@@

\DefMacro{retrain_debug_retrained_lc_62}{simple negations: not neutral is still neutral}

@@

\DefMacro{retrain_debug_retrained_lc_63}{simple negations: not neutral is still neutral}

@@

\DefMacro{retrain_debug_retrained_lc_64}{neutral words in context}

@@

\DefMacro{retrain_debug_retrained_lc_65}{neutral words in context}

@@

\DefMacro{retrain_debug_retrained_lc_66}{neutral words in context}

@@

\DefMacro{retrain_debug_retrained_lc_67}{neutral words in context}

@@

\DefMacro{retrain_debug_retrained_lc_68}{neutral words in context}

@@

\DefMacro{retrain_debug_retrained_lc_69}{neutral words in context}

@@

\DefMacro{retrain_debug_retrained_lc_70}{neutral words in context}

@@

\DefMacro{retrain_debug_retrained_lc_71}{my opinion is what matters}

@@

\DefMacro{retrain_debug_retrained_lc_72}{my opinion is what matters}

@@

\DefMacro{retrain_debug_retrained_lc_73}{my opinion is what matters}

@@

\DefMacro{retrain_debug_retrained_lc_74}{my opinion is what matters}

@@

\DefMacro{retrain_debug_retrained_lc_75}{my opinion is what matters}

@@

\DefMacro{retrain_debug_retrained_lc_76}{my opinion is what matters}

@@

\DefMacro{retrain_debug_retrained_lc_77}{my opinion is what matters}

@@

\DefMacro{retrain_debug_retrained_lc_78}{Sentiment-laden words in context}

@@

\DefMacro{retrain_debug_retrained_lc_79}{Sentiment-laden words in context}

@@

\DefMacro{retrain_debug_retrained_lc_80}{Sentiment-laden words in context}

@@

\DefMacro{retrain_debug_retrained_lc_81}{Sentiment-laden words in context}

@@

\DefMacro{retrain_debug_retrained_lc_82}{Sentiment-laden words in context}

@@

\DefMacro{retrain_debug_retrained_lc_83}{Sentiment-laden words in context}

@@

\DefMacro{retrain_debug_retrained_lc_84}{Sentiment-laden words in context}

@@

\DefMacro{retrain_debug_retrained_lc_85}{Hard: Negation of positive with neutral stuff in the middle (should be negative)}

@@

\DefMacro{retrain_debug_retrained_lc_86}{Hard: Negation of positive with neutral stuff in the middle (should be negative)}

@@

\DefMacro{retrain_debug_retrained_lc_87}{Hard: Negation of positive with neutral stuff in the middle (should be negative)}

@@

\DefMacro{retrain_debug_retrained_lc_88}{Hard: Negation of positive with neutral stuff in the middle (should be negative)}

@@

\DefMacro{retrain_debug_retrained_lc_89}{Hard: Negation of positive with neutral stuff in the middle (should be negative)}

@@

\DefMacro{retrain_debug_retrained_lc_90}{Hard: Negation of positive with neutral stuff in the middle (should be negative)}

@@

\DefMacro{retrain_debug_retrained_lc_91}{Hard: Negation of positive with neutral stuff in the middle (should be negative)}

@@

\DefMacro{retrain_debug_retrained_lc_92}{['Q & A: yes'  'Q & A: yes (neutral)']}

@@

\DefMacro{retrain_debug_retrained_lc_93}{['Q & A: yes'  'Q & A: yes (neutral)']}

@@

\DefMacro{retrain_debug_retrained_lc_94}{['Q & A: yes'  'Q & A: yes (neutral)']}

@@

\DefMacro{retrain_debug_retrained_lc_95}{['Q & A: yes'  'Q & A: yes (neutral)']}

@@

\DefMacro{retrain_debug_retrained_lc_96}{['Q & A: yes'  'Q & A: yes (neutral)']}

@@

\DefMacro{retrain_debug_retrained_lc_97}{['Q & A: yes'  'Q & A: yes (neutral)']}

@@

\DefMacro{retrain_debug_retrained_lc_98}{['Q & A: yes'  'Q & A: yes (neutral)']}

>>>>

\DefMacro{retrain_debug_retrained_lc_50}{Sentiment change over time, present should prevail}

@@

\DefMacro{retrain_debug_retrained_lc_51}{Sentiment change over time, present should prevail}

@@

\DefMacro{retrain_debug_retrained_lc_52}{Sentiment change over time, present should prevail}

@@

\DefMacro{retrain_debug_retrained_lc_53}{Sentiment change over time, present should prevail}

@@

\DefMacro{retrain_debug_retrained_lc_54}{Sentiment change over time, present should prevail}

@@

\DefMacro{retrain_debug_retrained_lc_55}{Sentiment change over time, present should prevail}

@@

\DefMacro{retrain_debug_retrained_lc_56}{Sentiment change over time, present should prevail}

@@

\DefMacro{retrain_debug_retrained_lc_57}{Negated neutral should still be neutral}

@@

\DefMacro{retrain_debug_retrained_lc_58}{Negated neutral should still be neutral}

@@

\DefMacro{retrain_debug_retrained_lc_59}{Negated neutral should still be neutral}

@@

\DefMacro{retrain_debug_retrained_lc_60}{Negated neutral should still be neutral}

@@

\DefMacro{retrain_debug_retrained_lc_61}{Negated neutral should still be neutral}

@@

\DefMacro{retrain_debug_retrained_lc_62}{Negated neutral should still be neutral}

@@

\DefMacro{retrain_debug_retrained_lc_63}{Negated neutral should still be neutral}

@@

\DefMacro{retrain_debug_retrained_lc_64}{Short sentences with neutral adjectives and nouns}

@@

\DefMacro{retrain_debug_retrained_lc_65}{Short sentences with neutral adjectives and nouns}

@@

\DefMacro{retrain_debug_retrained_lc_66}{Short sentences with neutral adjectives and nouns}

@@

\DefMacro{retrain_debug_retrained_lc_67}{Short sentences with neutral adjectives and nouns}

@@

\DefMacro{retrain_debug_retrained_lc_68}{Short sentences with neutral adjectives and nouns}

@@

\DefMacro{retrain_debug_retrained_lc_69}{Short sentences with neutral adjectives and nouns}

@@

\DefMacro{retrain_debug_retrained_lc_70}{Short sentences with neutral adjectives and nouns}

@@

\DefMacro{retrain_debug_retrained_lc_71}{Author sentiment is more important than of others}

@@

\DefMacro{retrain_debug_retrained_lc_72}{Author sentiment is more important than of others}

@@

\DefMacro{retrain_debug_retrained_lc_73}{Author sentiment is more important than of others}

@@

\DefMacro{retrain_debug_retrained_lc_74}{Author sentiment is more important than of others}

@@

\DefMacro{retrain_debug_retrained_lc_75}{Author sentiment is more important than of others}

@@

\DefMacro{retrain_debug_retrained_lc_76}{Author sentiment is more important than of others}

@@

\DefMacro{retrain_debug_retrained_lc_77}{Author sentiment is more important than of others}

@@

\DefMacro{retrain_debug_retrained_lc_78}{Short sentences with sentiment-laden adjectives}

@@

\DefMacro{retrain_debug_retrained_lc_79}{Short sentences with sentiment-laden adjectives}

@@

\DefMacro{retrain_debug_retrained_lc_80}{Short sentences with sentiment-laden adjectives}

@@

\DefMacro{retrain_debug_retrained_lc_81}{Short sentences with sentiment-laden adjectives}

@@

\DefMacro{retrain_debug_retrained_lc_82}{Short sentences with sentiment-laden adjectives}

@@

\DefMacro{retrain_debug_retrained_lc_83}{Short sentences with sentiment-laden adjectives}

@@

\DefMacro{retrain_debug_retrained_lc_84}{Short sentences with sentiment-laden adjectives}

@@

\DefMacro{retrain_debug_retrained_lc_85}{Negated positive with neutral content in the middle}

@@

\DefMacro{retrain_debug_retrained_lc_86}{Negated positive with neutral content in the middle}

@@

\DefMacro{retrain_debug_retrained_lc_87}{Negated positive with neutral content in the middle}

@@

\DefMacro{retrain_debug_retrained_lc_88}{Negated positive with neutral content in the middle}

@@

\DefMacro{retrain_debug_retrained_lc_89}{Negated positive with neutral content in the middle}

@@

\DefMacro{retrain_debug_retrained_lc_90}{Negated positive with neutral content in the middle}

@@

\DefMacro{retrain_debug_retrained_lc_91}{Negated positive with neutral content in the middle}

@@

\DefMacro{retrain_debug_retrained_lc_92}{parsing sentiment in (question, yes) form}

@@

\DefMacro{retrain_debug_retrained_lc_93}{parsing sentiment in (question, yes) form}

@@

\DefMacro{retrain_debug_retrained_lc_94}{parsing sentiment in (question, yes) form}

@@

\DefMacro{retrain_debug_retrained_lc_95}{parsing sentiment in (question, yes) form}

@@

\DefMacro{retrain_debug_retrained_lc_96}{parsing sentiment in (question, yes) form}

@@

\DefMacro{retrain_debug_retrained_lc_97}{parsing sentiment in (question, yes) form}

@@

\DefMacro{retrain_debug_retrained_lc_98}{parsing sentiment in (question, yes) form}
